\chapter{\abstractname}

\paragraph{Good software architecture documentation paves the way for a good software practice, making the software itself more maintainable, extendable and sustainable over its extended lifetime and evolution. A complex open-source software that grows exponentially with time, requires this documentation to serve the purpose of  knowledge sharing for new developers, communicate software architecture rationale to the users and other stakeholders and serve as means for documenting the ideas behind the design of architectural components and their interfaces.}
\paragraph{The thesis involves the initial research of the available state-of-the-art Software Architecture documentation processes, tools, etc. that help in maintaining software architecture documentation and keeping it consistent with the evolving architecture. Understanding the current software architecture documentation process at Mediawiki while keeping the evaluation goals in mind is an essential part of this thesis work. It also focuses on critical evaluation of the existing documentation process to derive requirements for its improvement.}
\paragraph{Based on the analysis, review and interaction method, an improved Software Architecture documentation process will be proposed, implemented and evaluated. Initial work involves understanding the MediaWiki software architecture complexities from an open social software perspective. Then existing software processes are studied in order to present ideas for a better maintainable software architecture documentation process. The final step is to evaluate improvements of the process and the quality of documentation produced following these improvements on grounds of maintainability, accessibility, consistency, completeness, etc.}
 



