\addcontentsline{toc}{chapter}{Acknowledgments}
\thispagestyle{empty}

\vspace*{2cm}

\begin{center}
{\usekomafont{section} Acknowledgments}
\end{center}

\vspace{1cm}

First and foremost, I would like to thank Prof. Dr. Florian Matthes for giving me the opportunity to write my Master thesis in the Software Engineering for Business Information Systems (SEBIS) chair at TU Munich. 
\\\indent This thesis topic was proposed and realized following the visionary ideas of Dr. Gero Scholz and Dr. Ernst Denert. I am very grateful for their valuable inputs, collaboration efforts and immense support that contributed to the successful completion of the thesis work. 
\\\indent I wholeheartedly thank my adviser Klym Shumaiev for his persistent motivation and the extensive advice and support throughout the course of this research work. 
\\\indent The thesis work was also supported by the MWDE (Mediawiki Deutschland) at Berlin with special reference to Mediawiki stakeholders Daniel Kinzler, S Page and Quim Gil who provided their timely consultation and feedback on the research and implementation work covered in this thesis.
\\\indent I want to specially thank all my friends who were directly or indirectly involved during the course of this thesis and took time to help me out and motivate me in my difficult times. I would like to specially thank my friend Uliana Bakhtina for her valuable inputs on technical issues and constant support. Also, I would like to extend my special token of thanks to my special friends : Amit R Desai, Snehalatha Radhakrishnan, Nitin Deshpande, Urmimala Chakroborty, Dip Nag, Anamika Choudhury; for being my strongest pillars of support.
\\\indent Last but not least, I thank my parents for always supporting and backing me up in all my endeavors.



\cleardoublepage{}
